The evolution of gene expression in the term placenta of viviparous mammals

### 2016-01-06 manuscript/manuscript.Rnw
add paragraph on spidermonkey

>>>>

For the term placenta of \smonkey, assembled contigs from RNA-seq were
aligned using against \human and the best alignment was chosen as the
annotation for each assembled contig. In the term placenta of
\smonkey, the top 50 non-housekeeping genes
(\cref{tab:top50_spider_monkey_placenta}) include a possible regulator
of androgen receptor signaling
\cite{Sampson.ea2012:PAGE4positivityisassociated}, \textit{PAGE4} %
(\ac{FPKM}=\Sexpr{gene.expression("ateles fusciceps","PAGE4")}), %
the pregnancy specific glycoprotein \textit{PSG8}
(\ac{FPKM}=\Sexpr{gene.expression("ateles fusciceps","PSG8")}), %
a member of the chorionic somatotropins, \textit{GH1} %
(\ac{FPKM}=\Sexpr{gene.expression("ateles fusciceps","GH1")}), %
a few HLA genes (\textit{HLA-A}, \textit{HLA-F},
\cref{tab:top50_spider_monkey_placenta}), and multiple components of
the annexin complex %
(\Sexpr{gene.expression("ateles fusciceps","ANXA2",complete=TRUE)}, %
\Sexpr{gene.expression("ateles fusciceps","S100P",complete=TRUE)}, %
\Sexpr{gene.expression("ateles fusciceps","S100A11",complete=TRUE)}) %
which may play a role in angiogenesis, and certainly regulate
cell-cell interaction in the developing placenta
\cite{Liu.ea2015:AnnexinA2complexeswith}.
